%-------------------------
% Hoang Nguyen's resume in LaTeX
% Github: https://github.com/hoangdesu
% Personal website: https://hoangdesu.com
% Last updated: Oct 2022
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItems}[3]{
  \item\small{
    \textbf{#1:} \\
        {#2} \\
        {#3}
    
  }
}

\newcommand{\normalResumeItem}[1]{
  \item\small{
    {#1}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Hoang Nguyen} & \href{https://hoangdesu.com/}{www.hoangdesu.com} \\
  \href{mailto:hoangdesu@gmail.com}{hoangdesu@gmail.com} & \href{https://github.com/hoangdesu}{github.com/hoangdesu} \\
  \href{tel:+84-913-172-602}{+84-913-172-602} & \href{https://www.linkedin.com/in/hoangdesu/}{linkedin.com/in/hoangdesu} \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {RMIT University Vietnam}{Ho Chi Minh City, Vietnam}
      {Bachelor of Science in Software Engineering}{Feb. 2018 -- Dec. 2022}
    \resumeSubheading
      {Pius X High School}{Lincoln, NE, U.S.A}
      {General education}{Sep. 2015 -- Jun. 2016}
  \resumeSubHeadingListEnd
  
 %
%--------PROGRAMMING SKILLS------------
\section{Technical skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Languages}{: Python, HTML/CSS, JavaScript, TypeScript, Java, Swift, Lua, Bash, C\#, C++, SQL}
   }
   \item{
    \textbf{Technologies}{: ReactJS, NextJS, NodeJS, Spring, GraphQL, AWS, Docker, Git, Jenkins, iOS, Android}
   }
   \item{
    \textbf{Experienced}{: Jest, Cucumber, WordPress, Winform, Game Development (Löve2D, PyGame, Unity, SwiftUI), MongoDB, PostgreSQL, Kafka, OpenCV, NumPy, Tkinter, JavaFx, SonarQube, LaTeX}
   }
 \resumeSubHeadingListEnd
 



%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {National Australia Bank}{Ho Chi Minh City, Vietnam}
      {Software Engineer}{Dec. 2021 -- present}
      \resumeItemListStart
        \resumeItems{Team member}
          {- Designed and developed multiple enterprise-level applications for the Open Data Engineering team, focusing on the front-end and the BFF levels with cloud-first approach; substantially using React, Node and GraphQL.}
          {- Continuous Integration Pipeline with Jenkins, pull requests, code reviews, agile development, unit testing, acceptance testing.}\\
          {- Represented the team to prepare and demonstrate for NAB Australia on the topic of mini-app development.} \\
          {- Enriched system metrics by integrating analytic utilities into current applications.}
        \resumeItem{Starcamper Batch 1}
          {Worked with a team called Titanium in a full-time training program provided by NAB Innovation Centre Vietnam (NICV) and graduated as a batch 1 Starcamper to get familiar with the technologies being used at NAB in order to facilitate the final Capstone project which resulted in an official employment with NICV.} \\
        %  \normalResumeItem
        %   {hi ya}
      \resumeItemListEnd

    \resumeSubheading
      {Live Italian Luxury}{Ho Chi Minh City, Vietnam}
      {Web Developer | Salesperson}{2018 -- 2020}
      \resumeItemListStart
        \normalResumeItem
            {Designed and developed websites for the company, focusing on importing Italian products and marketing in Vietnamese market.}
        \normalResumeItem    
            {Managed products, product campaigns and online contents with Search Engine Optimized solutions using tools like HTML/CSS/JavaScript and CMS such as WordPress and Squarespace.}
        \normalResumeItem 
            {Various notable websites including \href{https://www.liveitalianluxury.com/}{https://www.liveitalianluxury.com} and \href{https://www.miceriumlab.net/}{https://www.miceriumlab.net}.}
     
      \resumeItemListEnd

    \resumeSubheading
      {Private Tutor}{Ho Chi Minh City, Vietnam}
      {Computer Science, Programming, IELTS}{2019 -- present}
      \resumeItemListStart
        \normalResumeItem
            {Work as a private tutor mainly for Programming and Computer Science subjects in spare time.}
        \normalResumeItem
            {Courses teaching: Python, Java, JavaScript, A-level Computer Science, AP Computer Science, Arduino, Scratch.}
        \normalResumeItem
        {Tutor a wide range of student groups, ranging from middle-school ages to university level.}
        \normalResumeItem{Notable achievements:}
            \\ {- Helped a student to earn a 100\% scholarship from Michigan University.}
            \\ {- Students are studying at Vinschool, Le Hong Phong, BIS, VAS, TAS, VFIS, RMIT Vietnam, Singapore (Nanyang, SIM), America (Michigan, George Mason), Canada (University of Waterloo).}
      
      
        % \resumeItem{Portfolio Management}
        %   {Created models for portfolio hedging,  portfolio optimization and price forecasting. Also creating a strategy backtesting engine used for simulating and backtesting strategies.}
        % \resumeItem{QuantDesk}
        %   {Python backend for a web application used by hedge fund managers for portfolio management.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
  
   %--------SOFT SKILLS------------
\section{Supplemental skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Languages}{ | Proficient: Vietnamese, English | Conversational: Japanese}
    %  \hfill
    %  \textbf{Conversational}{: Japanese}
   }
   \item{
        \textbf{Design and media}{ | UI/UX, Figma, Sketch, Invision, Photoshop, Premiere, Illustrator, Final Cut Pro}
   }
 \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
